### 2013-05-31 doc/nips2013/setup.tex
made a pass up through section 4 (measurements)

In the directed case, we assume a directed acyclic graph over $V$,
and define $\pi(j) \subset V$ to be the parents of each node $j \in V$.
Next, define a model as a product of locally-normalized models:
\begin{align}
  p_\theta(z) = \prod_{j \in V} p_\theta(z_j \mid z_{\pi(j)}), \quad\quad
  p_\theta(z_j \mid z_{\pi(j)}) = \exp \{ \phi_j(z_j, z_{\pi(j)})^\top\theta - A_j(\theta; z_{\pi(j)}) \}.
\end{align}
Here, each local model has its own local features $\phi_j(z_j, z_{\pi(j)})$
and its own local log-partition function $A(\theta; z_{\pi(j)})$, which depends on values of its parent.
To make the directed and undirected models more comparable,
define $\phi(z) = \sum_{j \in V} \phi(z_j, z_{\pi(j)})$
and $A(\theta; z) = \sum_{j \in V} A_j(\theta; z_{\pi(j)})$,
so that:
\begin{align}
  p_\theta(z) \eqdef \exp\{ \phi(z)^\top\theta - A(\theta; z) \}. \aside{directed}
\end{align}

@@

% Statement
This paper focuses on the problem of parameter estimation:
We are given $n$ i.i.d.~examples of the observed variables $D = (x^{(1)}, \dots, x^{(n)})$
where each $x^{(i)} \sim p_{\theta^*}$ for some true parameters $\theta^*$.
Our goal is to produce a parameter estimate $\hat\theta$ which is hopefully
close to $\theta^*$.

>>>>

In the directed case, we assume a directed acyclic graph over $V$,
and define $\pi(j) \subset V$ to be the parents of each node $j \in V$.
Next, define a model as a product of locally-normalized models:
\begin{align}
  p_\theta(z) = \prod_{j \in V} p_\theta(z_j \mid z_{\pi(j)}), \quad\quad
  p_\theta(z_j \mid z_{\pi(j)}) = \exp \{ \phi_j(z_j, z_{\pi(j)})^\top\theta - A_j(\theta; z_{\pi(j)}) \}.
\end{align}
Here, each local model has its own local features $\phi_j(z_j, z_{\pi(j)})$
and its own local log-partition function $A(\theta; z_{\pi(j)})$, which depends on values of its parent.
To consolidate notation,
define $\phi(z) = \sum_{j \in V} \phi(z_j, z_{\pi(j)})$
and $A(\theta; z) = \sum_{j \in V} A_j(\theta; z_{\pi(j)})$,
so that:
\begin{align}
  p_\theta(z) \eqdef \exp\{ \phi(z)^\top\theta - A(\theta; z) \}. \aside{directed}
\end{align}

@@

% Statement
This paper focuses on the problem of parameter estimation:
We are given $n$ i.i.d.~examples of the observed variables $D = (x^{(1)}, \dots, x^{(n)})$
where each $x^{(i)} \sim p_{\theta^*}$ for some true parameters $\theta^*$.
Our goal is to produce a parameter estimate $\hat\theta$ that approximates $\theta^*$.
